### 2014-09-25 thesis/experiments/experiments.tex
Wrote more of the experimental setup

We used the WEKA \citep{Hall2009} implementation of the above methods, after
converting the data into the Attribute-Relation File Format
(ARFF)\footnote{\url{http://weka.wikispaces.com/ARFF+\%28developer+version\%29}}
most suitable for the program.
\todo{give more details, ie specifying binary/numeric
attributes, maybe specify in appendix?}

@@

\section{Model construction}

\subsection{Single classifier}

\subsubsection{Parameter tuning}

@@

\section{Performance evaluation} % don't forget cross-validation

>>>>

We used the WEKA 3.7.11 \citep{Hall2009} implementation of the above
methods, after converting the data into the Attribute-Relation File Format
(ARFF)\footnote{\url{http://weka.wikispaces.com/ARFF+\%28developer+version\%29}}
most suitable for the program.
\todo{give more details, ie specifying binary/numeric
attributes, maybe specify in appendix?}

@@

Altogether, the various feature selection methods resulted in a total of
7 data sets (4 automated, 2 expert selected, and 1 with all features) which
we used in the model construction phase.

\section{Model construction}
Here we present the various classification schemes we used in order to find
the best model for the trauma LOS data.

\subsection{Single classifier}
First we sought to compare the suitability and performance of various
classifiers by themselves (later we looked at \textit{ensembles} of
classifiers, when more than one is involved in making a prediction).
These are the
classifiers studied: \todo{expand a bit more here, maybe list the
configuration parameters}
\begin{itemize}
\item Na\"{i}ve Bayes
\item Decision tree (C4.5)
\item Logistic regression
\item Support vector machine
\item $K$-nearest neighbour
\item Feed-forward neural network (multilayer perceptron)
\end{itemize}

Each classifier was trained using ten-fold cross-validation for each of the
7 data sets obtained from the various feature selection methods described
above. This was repeated 30 times for each classifier and the reasons for
this, as well as the metrics used to assess the performance of these
classifiers, are described in Section \ref{sec:perfeval} of this chapter.

In addition to the feature selection methods, we also used the WEKA 3.7.11
\citep{Hall2009} implementation of the above classifiers for our experiments.
Training was automated using a Bash shell script (whose source can be found
in the appendix) that programmatically read in a list of classifiers to
train and repeated the procedure any specified number of times, writing the
results to a specified directory for later reference.

\subsubsection{Parameter tuning}
It is difficult in data mining to apply an algorithm out-of-the-box and have
it perform optimally on a given data set \citep{Witten2005}. Therefore, time
must be spent tweaking and tuning the parameters of a classifier in order to
improve classification performance. This was the next step we took. We
considered a range of values for various parameters of each classification
scheme, and tried some of these new configurations by hand and some by using
WEKA's cross-validation parameter selection class. The configurations tested,
as well as how they were executed, are listed in this table:
\todo{insert table!}

@@

\section{Performance evaluation} % don't forget cross-validation
\label{sec:perfeval}
